{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-22 paper/paper.tex
added defintion of the next function

>>>>

To make this distinction a new type system is introduced. Type judgments have the form
$\vdash_\alpha [c]_{\alpha'}^n : E$, where $E$ is a function that maps labels to security
levels.\footnote{Given $E$ it is easy to define a security environment $se$. For a definition
of $E$ see Barthe et. al. 2006} $\alpha$ denotes if $c$ is \textit{part of} a branching
instruction that branches on secret ($\bullet$) or public ($\circ$) data and $\alpha'$ is the
security level of the guard \textit{in} the branching instruction.

We now take a look at the rules of this type system concerning the \texttt{if} instruction.

\todo{use an other package to display these rules}
\begin{figure}
\begin{prooftree}
\AxiomC{$\vdash e : L$}
\AxiomC{$\vdash_\alpha c : E$}
\AxiomC{$\vdash_\alpha c' : E$}
\LeftLabel{L-COND:\quad}
\TrinaryInfC{$\vdash_\alpha [if \ e \ then \ c \ else \ c']^n_\alpha : E$}
\end{prooftree}

\begin{prooftree}
\AxiomC{$\vdash e : H$}
\AxiomC{$\vdash_\bullet c : E$}
\AxiomC{$\vdash_\bullet c' : E$}
\LeftLabel{H-COND:\quad}
\TrinaryInfC{$\vdash_\bullet [if \ e \ then \ c \ else \ c']^n_\bullet : E$}
\end{prooftree}

\begin{prooftree}
\AxiomC{$\vdash e : H$ \quad $\vdash_\bullet c : E$}
\AxiomC{$\vdash_\bullet c' : E$}
\AxiomC{$E = lift_H(E, sregion(n))$}
\LeftLabel{TOP-H-COND:\quad}
\TrinaryInfC{$\vdash_\circ [if \ e \ then \ c \ else \ c']^n_\bullet : E$}
\end{prooftree}

\caption{Typing rules for \texttt{if} on source level.}
\label{fig:typing-rules-if}
\end{figure}

The first rule L-COND from Figure \ref{fig:typing-rules-if} says that if we branch on a low
guard, everything depends on the security level of $c$ and $c'$. The rule H-COND covers the
case where we have a high guard, in this case the control dependence region has to be marked
high. The rule TOP-H-COND is the interesting one. Because of the preceding rules we can not
be part of branch with a low guard, therefore we are in the outermost high branch. The premise
$E' = lift_H(E, sregion(n))$ reads as: For all labels in the control dependence region $E$ is
defined as $E'(n) = H \sqcup E(n)$ and $E'(n) = E(n)$ for all other labels.

This type system is powerful enough to prevent explicit and implicit flows and can therefor
replace the type system defined previously. \todo{show ASSIGN rule?}

With this type system in mind, we can now define our \texttt{next} function.

\begin{definition}{next}
For every branching point $c$ in the source program such that $\vdash_\circ [c]_\bullet^n$, we  have
that $\forall k \in tregion(n) . next(k) = jun(n)$.
\end{definition}
